Rotation effects on the Lyman-$\alpha$ line morphology in distant galaxies

### 2013-05-31 paper/Analisis.tex
2 paragraphs in Inhomogeneous section + plots :)

Now we set up a test model when the photons are placed in an inhomogeneous model,

>>>>

As we know there is unlikely to find galaxies with radiation sources 
distributed homogeneously. Most of them are in a clumpy distribution 
(Larsen et al 2013*) which affected the resulting spectra. In order 
to study an inhomogeneous distribution we set up a model in which we 
select certain photons that are placed in a specific place but that 
are not symmetrically Fig.~\ref{figure:distributions}.

\begin{figure*}
  \includegraphics[width=0.45\textwidth]{Distribution1.png}
  \includegraphics[width=0.45\textwidth]{Distribution2.png}
 \caption{Inhomogeneous distributions of 
 photons, red area are the selected photons, the arrow points to the 
 observer position, left panel Distribution 1, right panel Distribution 2\label{figure:distributions}} 
\end{figure*}

In Fig.~\ref{figure:inhomogeneous} we show the resulting spectra of 
distribution 1 and 2, the most important result is to see the 
asymmetry  of the line in particular the photons selected in 
distribution 1 present a blueshift while photons selected in 
distribution 2 present a redshift. Is also important to see that
as velocity increases this shifts became stronger.

\begin{figure*}
  \includegraphics[width=0.45\textwidth]{InomogeneousModelt5.png}
  \includegraphics[width=0.45\textwidth]{InomogeneousModelt6.png}
 \caption{Inhomogeneous model for velocities $50km/s$ and $300km/s$ , left panel with $\tau=10^5$, right panel with $\tau=10^5$\label{figure:inhomogeneous}} 
\end{figure*}
